\documentclass[10pt,a4paper]{article}

% Geometry: bottom margin enlarged for the GDPR footer
\usepackage[a4paper,margin=2.5cm,bottom=3cm]{geometry}

% Fonts: lmodern is a sharper sans-serif. We render the whole document in
% sans-serif to match the markdown bold/italic look on screen.
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

% Section formatting: subsection (h2 in MD) is Large+bold+uppercase + border,
% matching main.tex:24. Section (h1 in MD — the name) is huge + centered.
\usepackage{titlesec}
\usepackage{xcolor}
\titleformat{\section}{\centering\Huge\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{0pt}{12pt}
\titleformat{\subsection}{\Large\bfseries\MakeUppercase}{}{0em}{}
\titlespacing*{\subsection}{0pt}{12pt}{6pt}
\setcounter{secnumdepth}{0}

\usepackage{parskip}
\usepackage{enumitem}
\setlist[itemize]{topsep=4pt,partopsep=0pt,itemsep=2pt,leftmargin=*}

% Tightlist: pandoc emits \tightlist for compact bullet lists. Provide a no-op
% definition that matches the default pandoc template.
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% hyperref: PDF metadata from YAML frontmatter (title/author/keywords).
% pandoc substitutes title-meta/author-meta/subject-meta/keywords automatically.
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={Paweł Jacek Frąckowiak --- Software Architect / Kubstronaut},
  pdfauthor={Paweł Jacek Frąckowiak},
  pdfkeywords={Software
Architect, Kubernetes, Go, Python, GenAI, Security, Platform
Engineering},
}

% GDPR footer block, verbatim from main.tex:30-49.
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\newcommand{\gdprText}{%
  \scriptsize \color{gray}
  I agree to the processing of personal data provided in this document for realising the recruitment process pursuant to the Personal Data Protection Act of 10 May 2018 (Journal of Laws 2018, item 1000) and in agreement with Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of natural persons with regard to the processing of personal data and on the free movement of such data, and repealing Directive 95/46/EC (General Data Protection Regulation).%
}
\fancyfoot[C]{\parbox{\textwidth}{\centering\gdprText}}
\fancypagestyle{plain}{%
  \fancyhf{}%
  \fancyfoot[C]{\parbox{\textwidth}{\centering\gdprText}}%
}

\begin{document}

\section{Paweł Jacek Frąckowiak}\label{paweux142-jacek-frux105ckowiak}

Wrocław, Poland ·
\href{mailto:pawelfrackowiak@protonmail.com}{\nolinkurl{pawelfrackowiak@protonmail.com}}
· \href{https://linkedin.com/in/pawelfrackowiak}{LinkedIn} ·
\href{https://github.com/pfrack}{GitHub} · \href{files/cv.pdf}{PDF}

\subsection{Professional Summary}\label{professional-summary}

Hands-on Software Architect and Kubstronaut with a strong foundation in
Quality Assurance and Automation. I combine deep infrastructure
expertise (Kubernetes, Go, Security) with practical application
development (Python, GenAI). I focus on moving AI projects from ``proof
of concept'' to stable, scalable production systems. My goal is to
engineer reliable platforms where code quality and operational security
are priorities, not afterthoughts.

\subsection{Experience}\label{experience}

\subsubsection{\texorpdfstring{Architect (Go, Python, GenAI) / Lead
Developer \emph{(Managing Solution
Architect)}}{Architect (Go, Python, GenAI) / Lead Developer (Managing Solution Architect)}}\label{architect-go-python-genai-lead-developer-managing-solution-architect}

\emph{Capgemini Polska Sp. z o.o., Wrocław, Mar 2022 -- Present}

\begin{itemize}
\tightlist
\item
  \textbf{SmartDesk (Document Intelligence):} Architected the on-premise
  infrastructure for an AI-driven data extraction platform processing
  complex documents (leases, resumes, certificates). Designed a
  hardware-aware pipeline using Docling (FastAPI) that toggles between
  CPU-bound \textbf{PaddleOCR} and GPU-bound \textbf{dots.mocr} based on
  hardware availability. Configured the BiFrost LLM gateway to
  dynamically route standard LLM requests to \textbf{Gemma 4} (served
  via vLLM) and specialized OCR workloads to the OCR model. Bridged the
  AI backend with a React/NestJS frontend, ensuring seamless operation
  across AWS cloud and secure bare-metal environments.
\item
  \textbf{Multi-Agent Architecture Consulting (Azure):} Acted as a
  Consulting Architect advising enterprise clients on the adoption of
  advanced AI patterns using the Microsoft Agentic Framework. Consulted
  on strategic implementation of an ``Agent Mesh'' architecture,
  demonstrating how a central orchestrator/planner agent can dynamically
  route tasks to specialized containerized agents via skill
  registration. Guided client integration strategy for leveraging Model
  Context Protocol (MCP) to autonomously execute complex workflows
  within \textbf{SAP} and \textbf{ServiceNow (SNow)} environments.
\item
  \textbf{GenAI Platform Architecture:} Architected a RAG-as-a-Service
  platform enabling employees to upload documents and interact
  conversationally. Designed end-to-end document pipeline using
  Unstructured AI (chunking), Azure AI Search, SharePoint, S3 buckets,
  DynamoDB, Lambda, Step Functions, SQS/SNS, EC2 instances, and API
  Gateway for secure self-service document processing.
\item
  \textbf{Kagent Research (DevOps AI):} Conducted in-depth research and
  proof-of-concept development for Kagent -- an AI agent framework
  specifically designed for DevOps workflows. Evaluated agentic patterns
  for automating infrastructure provisioning, CI/CD pipeline
  optimization, and Kubernetes cluster management using advanced LLM
  orchestration techniques.
\item
  \textbf{High-Performance Backend (Go):} Tech Lead for the
  \emph{Digital Euro} integration layer. Engineered a secure,
  low-latency system integrating HSM, caching strategies, DESP
  Interface, and Kubernetes to handle financial transaction standards.
\item
  \textbf{GenAI Strategy \& Consulting:} Acting Architect in the GenAI
  Expert Center, advising projects on ``Build vs.~Buy'' strategies.
  Evaluated when to deploy custom private models (vLLM, Ollama) versus
  leveraging existing internal company assets or cloud APIs, balancing
  security, cost, and compliance.
\item
  \textbf{Enterprise Security Integration:} Contributed to development
  of a Go-based Key Management System (KMS) for SAP BTP. Implemented
  critical gRPC/OAuth2 components to enable secure cryptographic
  operations in a cloud-native environment.
\item
  \textbf{Project Leadership \& Mentoring:} Led dynamic project-based
  engineering teams across Go/Python streams. Managed recruitment
  processes and guided strategic migration from legacy RPA to modern
  Power Platform architectures.
\item
  \textbf{Specialized Domain Applications:} Developed critical tools for
  clients, including a nuclear waste calculation engine (Python/Pandas)
  and productivity add-ins (TypeScript/Node.js) for the MS Office
  ecosystem.
\end{itemize}

\subsubsection{\texorpdfstring{Architect (Go, RPA) / Lead Developer
\emph{(Senior App.
Consultant)}}{Architect (Go, RPA) / Lead Developer (Senior App. Consultant)}}\label{architect-go-rpa-lead-developer-senior-app.-consultant}

\emph{Capgemini Polska Sp. z o.o., Wrocław, Jan 2020 -- Mar 2022}

\begin{itemize}
\tightlist
\item
  \textbf{Go Ecosystem Pioneer:} Spearheaded the first commercial Golang
  initiative in the Wrocław branch. Architected the core development
  ecosystem from ground zero, delivering critical tooling (OpenAPI
  transpilers) and a containerized test framework (Resty, Godog),
  effectively proving Go's viability for enterprise delivery.
\item
  \textbf{Intelligent Automation \& DevOps:} Tech Lead for the RPA
  Center of Excellence. Pioneered the use of \textbf{Jenkins as a Robot
  Orchestrator} and integrated UiPath with AI systems for a ``Level 1.5
  Support'' platform, bridging classic RPA with CI/CD practices.
\item
  \textbf{Process Intelligence:} Supported business optimization
  initiatives using Process Mining tools (Celonis, Qlik) to identify
  automation bottlenecks and validate solution designs (SDD/PDD) with
  real data.
\item
  \textbf{Custom Integration Modules:} Developed advanced UiPath
  activities in C\# (WPF) to bridge automation gaps, enabling secure SSH
  connections, advanced text parsing, and high-performance API
  integrations unavailable in standard libraries.
\item
  \textbf{Technical Recruitment \& Mentoring:} Acted as the primary
  technical recruiter and mentor for a 12-member team, defining coding
  standards and training the first wave of developers in the new tech
  stack.
\end{itemize}

\subsubsection{\texorpdfstring{Lead Automation Engineer \emph{(Senior
Test
Consultant)}}{Lead Automation Engineer (Senior Test Consultant)}}\label{lead-automation-engineer-senior-test-consultant}

\emph{Capgemini Polska Sp. z o.o., Wrocław, Jan 2019 -- Jun 2020}

\begin{itemize}
\tightlist
\item
  \textbf{Framework Development (Selenium):} Designed and maintained a
  custom Java-based Selenium automation framework (JUnit 5),
  establishing reusable test patterns and stable execution pipelines.
\item
  \textbf{Automation Strategy:} Defined and executed the test automation
  approach across teams, improving test coverage and reliability of
  regression runs.
\item
  \textbf{Performance Engineering:} Conducted performance analysis and
  load testing to identify system bottlenecks and provide actionable
  recommendations.
\end{itemize}

\subsubsection{Technical Trainer (Python \&
Selenium)}\label{technical-trainer-python-selenium}

\emph{Testuj.pl, Wrocław, Dec 2018 -- Apr 2019}

\begin{itemize}
\tightlist
\item
  \textbf{Expert Training Lead:} Conducted specialized weekend workshops
  and corporate training sessions on Test Automation using Python and
  Selenium WebDriver.
\item
  \textbf{Curriculum Development:} Designed practical coding exercises
  and training materials to upskill professional QA engineers.
\end{itemize}

\subsubsection{\texorpdfstring{Lead Automation Engineer (Embedded Web)
\emph{(Senior Test
Engineer)}}{Lead Automation Engineer (Embedded Web) (Senior Test Engineer)}}\label{lead-automation-engineer-embedded-web-senior-test-engineer}

\emph{Silicon \& Software Systems Polska Sp. z o.o., Wrocław, Dec 2015
-- Dec 2018}

\begin{itemize}
\tightlist
\item
  \textbf{Scale \& Reliability:} Managed a daily execution pipeline of
  \textasciitilde4,000 tests, combining high-level GUI validation with
  low-level embedded verification.
\item
  \textbf{Hybrid Framework Architecture:} Architected a dual-layer
  automation ecosystem: a Java/Selenium framework for web interfaces and
  Python-based scripting for direct embedded device testing and hardware
  interaction.
\item
  \textbf{Technical Leadership:} Led the comprehensive testing strategy
  for complex embedded systems, bridging the gap between hardware and
  software QA.
\end{itemize}

\subsubsection{Software Test Engineer}\label{software-test-engineer}

\emph{Fara Polska Sp. z o.o., Warsaw, Nov 2013 -- Nov 2015}

\subsubsection{R\&D Specialist / Test
Engineer}\label{rd-specialist-test-engineer}

\emph{Telekomunikacja Polska S.A. (Orange Labs), Jun 2009 -- Oct 2013}

\begin{itemize}
\tightlist
\item
  \textbf{Lab Automation \& R\&D:} Automated hardware/software testing
  workflows for telecommunication systems, reducing cycle time by
  \textasciitilde30\%. Managed laboratory infrastructure and executed
  complex test protocols.
\end{itemize}

\subsection{Education}\label{education}

\subsubsection{Postgraduate Studies in
E-Business}\label{postgraduate-studies-in-e-business}

\emph{Warsaw University of Technology, Poland, 2010}

\begin{itemize}
\tightlist
\item
  Focus: E-business strategies, internet technologies, and digital
  commerce models.
\end{itemize}

\subsubsection{M.Sc. Eng. in Electronics and
Telecommunications}\label{m.sc.-eng.-in-electronics-and-telecommunications}

\emph{Poznań University of Technology, Poland, 2008}

\begin{itemize}
\tightlist
\item
  Specialization: Information Transport Networks
\item
  Thesis: ``P2P in 4G Mobile Networks'' (Radio Communication Dept.).
  Developed a C++ simulation of the MAC Layer P2P mode for the WINNER
  system, focusing on network performance analysis.
\end{itemize}

\subsection{Key Certifications \&
Awards}\label{key-certifications-awards}

\begin{itemize}
\item
  \textbf{Kubernetes Ecosystem (Kubstronaut):} CKS (Oct 2025), KCSA (Nov
  2025), CKAD (Jul 2025), CKA (Dec 2024), KCNA (Aug 2025). Awarded the
  \textbf{Kubstronaut} title for holding all 5 CNCF certifications
  simultaneously
\item
  \textbf{Cloud \& Architecture:} Google Cloud Professional Cloud
  Architect (Dec 2023), Capgemini Certified Architect (Feb 2022).
\item
  \textbf{Other:} UiPath RPA Developer Advanced (Nov 2019), ISTQB
  Advanced Level Technical Test Analyst (Oct 2014), ITIL Foundation (Oct
  2021).
\end{itemize}

\subsection{Technical Skills}\label{technical-skills}

\begin{itemize}
\tightlist
\item
  \textbf{Core Languages:} Golang, Python, Bash/Shell Scripting
\item
  \textbf{Cloud Native \& DevOps:} Kubernetes (Kubstronaut), Docker,
  Helm, Terraform, Ansible, AWS (Lambda, ECS, DynamoDB), Azure AI,
  Google Cloud (GCP), CI/CD (Jenkins, GitHub Actions), Linux
  Administration
\item
  \textbf{AI \& LLM Engineering:} LangChain, vLLM, Ollama, Hugging Face,
  LocalAI, RAG Architectures, Vector Databases, BiFrost, Docling,
  PaddleOCR, dots.mocr, Microsoft Agentic Framework, MCP
\item
  \textbf{Backend \& Integration:} FastAPI, gRPC, REST API Design,
  OpenAPI/Swagger, AsyncAPI, OAuth2, HSM Integration, NestJS, React
\item
  \textbf{Automation \& Quality:} Pytest, Go Testify, Godog, Performance
  Testing, Integration Testing
\item
  \textbf{Leadership:} Technical Team Leadership, Solution Architecture,
  Mentoring, Agile/Scrum, Recruitment
\item
  \textbf{Prior Engineering Focus:} C++, Java, C\#, Selenium WebDriver,
  UiPath (RPA), Process Mining (Celonis)
\end{itemize}

\subsection{Languages}\label{languages}

\textbf{Polish}: Native \textbar{} \textbf{English}: Advanced (C1/C2)
\textbar{} \textbf{German}: Intermediate

Last updated: June 2026

\end{document}
